\documentclass{exam}
\begin{document}

\hfill\makebox[1in][r]{\vspace{.1in}Score: \rule{.5in}{1pt}}
\begin{center}
  \mbox{\mbox{\centering
    {\Large Cyber Summer Camp 2.0 Pre \& Post Knowledge Survey}.}}
\end{center}
\vspace{.2in}
\makebox[\textwidth]{Name: \enspace\hrulefill}

\begin{questions}
 
  \question Why is it a good idea to use a Virtual Machine?
    \begin{choices}
      \choice Protects the Host computer.
      \choice Greater utilization of hardware.
      \choice Because it will increase the likely hood of Skynet.
      \choice Can easily 'spin up' various types of OS's as needed.
    \end{choices}
  
    \question What is the root directory in Linux (similar to Windows C:\\\\ drive?
    \begin{choices}
      \choice \\root
      \choice \\home\\username
      \choice \\
      \choice Root:\\\\ 
    \end{choices}
  
    \question What is the difference between the commands: 'who' \& 'whoami'?
    \begin{choices}
      \choice No difference.
      \choice 'who' shows who is logged on; 'whoami' tells me the username of my EUID.
      \choice 'who' is short for 'whoami'. 
      \choice 'whoami' shows the 'who' for everyone logged on.
    \end{choices}
  
  \question The one secure way to remotely administer a computer is \rule{1in}{1pt}.
    \begin{choices}
      \choice telnet
      \choice FTP; 
      \choice RLogin/Rsh;
      \choice SSH;
    \end{choices}
  
  \question In Ubuntu, a list of all users for the system can be found at \rule{1in}{1pt}. 
    \begin{choices}
      \choice /etc/passwd
      \choice /etc/users
      \choice /home/users
      \choice /usr
    \end{choices}
  
    \question Explain an IP address (for your computer). 
    \begin{choices}
      \choice Similair to an TCP/UDP port. 
      \choice An address for a computer that can change.
      \choice An address for a computer that can never change.
      \choice Similair to a MAC address. 
    \end{choices}
  
  \newpage
  \question What port does an http (web) server listen on?
    \begin{choices}
      \choice 1 
      \choice 22
      \choice 80
      \choice 443
    \end{choices}
  
  \question What does this UFW command do?
  \begin{verbatim}
  TODO - PUT IN COMMAND
    int index;
    for(index = 0; index <= 7; index++){
      //Do Something...
    }
  \end{verbatim}
    \begin{choices}
      \choice 0 
      \choice 6
      \choice 7
      \choice 8
    \end{choices}
  
  \question The base design of a webpage is commonly written in?
    \begin{choices}
      \choice .com
      \choice www
      \choice HTTP
      \choice HTML
    \end{choices}

  \question Which choice will list all processes and then end process 1234? 
    \begin{choices}
      \choice ls -all; cd 1234
      \choice pwd; cat 1234
      \choice ps -e; kill 1234
      \choice who -all; rm 1234
    \end{choices}
  
  \end{questions}
\end{document}
